Impact of grids and dynamical cores in CESM2.2 on the meteorology and climate of the Arctic

### 2021-10-14 arcticgrids.tex
new racmo version
new climo smb components figure

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_diffRACMO23p2_5p5km.pdf}
\end{center}
\caption{Climatological (1979-1998) annual precipitation rate bias relative to the RACMO3.2p2 5.5km resolution data product \cite{NETAL2019SCIENCE}.}
\label{fig:prect}
\end{figure}

@@

>>>>

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_diffRACMO23p2_5p5km.pdf}
\end{center}
\caption{Climatological (1979-1998) annual precipitation rate bias relative to the RACMO2.3p2 5.5km resolution data product \cite{NETAL2019SCIENCE}.}
\label{fig:prect}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_climo_GRIS.pdf}
\end{center}
\caption{.}
\label{fig:climo}
\end{figure}
